---
title: "hnrnpk ChIPseq vs SNR - Cs ONLY"
author: "Des"
date: "`r Sys.Date()`"
output:
 html_document:
    pdf_print: paged
    toc: yes
    toc_depth: '3'
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# background/motivation

-  examine relationship between *in vitro* (i-Motif array SNR) binding and *in vivo* binding (ChIP-seq read density) of i-Motif probe sequences
-   for each i-Motif probe sequence, compute a score representing the binding of HNRPNK *in vivo* - in this case we use the maximum (or mean) read density observed across all ChIP-seq peaks containing the probe sequence

- keep in mind:  we're comparing double stranded (ChIP-seq) vs. single-stranded (array) data, so perhaps just focus on C's only

```{r loadlibraries}
library(dplyr)
library(purrr)
library(readr)
library(ggplot2)

```

```{r loaddata}
file<-'counts/iMotif_array_v2_HNRNPK_motif_analysis.invivo_scores.tsv'
data<-read.csv(file, sep='\t')
glimpse(data)

data<-data[data$hg38_occurrences >0,]
data<-data[grep("Cs",data$SeqClass),]
data1<-data[data$count.HNRNPK_HepG2.ENCFF035OPG.merged>0, c('UniqueID','SeqClass','hnRNPK_rep','HNRNPK_HepG2.ENCFF035OPG.merged.max_peak_score','HNRNPK_HepG2.ENCFF035OPG.merged.mean_peak_score')]
names(data1)<-c('UniqueID','SeqClass','Array_SNR','max_peak_read_density','mean_peak_read_density')



data1$Exp<-'HNRNPK_HepG2'
data2<-data[data$count.HNRNPK_K562.ENCFF505RNR.merged>0,c('UniqueID','SeqClass','hnRNPK_rep','HNRNPK_K562.ENCFF505RNR.merged.max_peak_score','HNRNPK_K562.ENCFF505RNR.merged.mean_peak_score')]
names(data2)<-c('UniqueID','SeqClass','Array_SNR','max_peak_read_density','mean_peak_read_density')
data2$Exp<-'HNRNPK_K562'
cdata<-rbind(data1,data2)

```

# SNR vs max chipseq score, faceted
```{r maxscore}


ggplot(data=cdata,aes(x=Array_SNR,y=max_peak_read_density))+ 
  facet_grid(cols=vars(Exp),scales='free_y') +
  geom_point(alpha=0.5) + 
  theme_bw() +
  ggpubr::stat_cor(method = "pearson", label.x = 30,label.y=400,show.legend = FALSE) +
  theme(aspect.ratio=1)

```

# SNR vs mean chipseq score faceted

```{r meanscore}


ggplot(data=cdata,aes(x=Array_SNR,y=mean_peak_read_density))+ 
  facet_grid(cols=vars(Exp),scales='free_y') +
  geom_point(alpha=0.5) + 
  theme_bw() +
  ggpubr::stat_cor(method = "pearson", label.x = 30,label.y=400,show.legend = FALSE) +
  theme(aspect.ratio=1)

```


# SNR vs max score, not faceted

```{r maxscore_nf, fig.height=4}


ggplot(data=data1,aes(x=Array_SNR,y=max_peak_read_density))+ 
  geom_point(alpha=0.5) + 
  theme_bw() +
  ggpubr::stat_cor(method = "pearson", label.x = 30,label.y=400,show.legend = FALSE) +
  theme(aspect.ratio=1) + 
  ylab('Max read density, HepG2') +
  xlab('Array SNR')


ggplot(data=data2,aes(x=Array_SNR,y=max_peak_read_density))+ 
  geom_point(alpha=0.5) + 
  theme_bw() +
  ggpubr::stat_cor(method = "pearson", label.x = 30,label.y=400,show.legend = FALSE) +
  theme(aspect.ratio=1) + 
  ylab('Max read density, K562') +
  xlab('Array SNR')

```

# SNR vs mean score, not faceted

```{r meanscore_nf, fig.height=4}


ggplot(data=data1,aes(x=Array_SNR,y=mean_peak_read_density))+ 
  geom_point(alpha=0.5) + 
  theme_bw() +
  ggpubr::stat_cor(method = "pearson", label.x = 30,label.y=400,show.legend = FALSE) +
  theme(aspect.ratio=1) + 
  ylab('Mean read density, HepG2') +
  xlab('Array SNR')


ggplot(data=data2,aes(x=Array_SNR,y=mean_peak_read_density))+ 
  geom_point(alpha=0.5) + 
  theme_bw() +
  ggpubr::stat_cor(method = "pearson", label.x = 30,label.y=400,show.legend = FALSE) +
  theme(aspect.ratio=1) + 
  ylab('Mean read density, K562') +
  xlab('Array SNR')

```

# max peak read density, separated by sequence class

```{r maxscore_seq, fig.height=8,fig.width=8}

ggplot(data=data1,aes(x=Array_SNR,y=max_peak_read_density,color=SeqClass))+ 
  geom_point(alpha=0.5) + 
  theme_bw() +
  facet_wrap(~SeqClass, nrow=1) + 
  ylab('Max read density, HepG2') +
  xlab('Array SNR')+
  theme(aspect.ratio=1) + 
  ggpubr::stat_cor(aes(label = after_stat(r.label)), label.x = 35,label.y=275,show.legend = FALSE) 


ggplot(data=data2,aes(x=Array_SNR,y=max_peak_read_density,color=SeqClass))+ 
  geom_point(alpha=0.5) + 
  theme_bw() +
  facet_wrap(~SeqClass, nrow=1) + 
  ylab('Max read density, K562') +
  xlab('Array SNR')+
  theme(aspect.ratio=1) + 

  ggpubr::stat_cor(aes(label = after_stat(r.label)), label.x = 35,label.y=350,show.legend = FALSE) 

```

# mean peak read density, separated by sequence class
```{r meanscore_seq, fig.height=8,fig.width=8}

ggplot(data=data1,aes(x=Array_SNR,y=mean_peak_read_density,color=SeqClass))+ 
  geom_point(alpha=0.5) + 
  theme_bw() +
  facet_wrap(~SeqClass, nrow=1) + 
  ylab('Mean read density, HepG2') +
  xlab('Array SNR')+
  theme(aspect.ratio=1) + 
  ggpubr::stat_cor(aes(label = after_stat(r.label)), label.x = 30,label.y=200,show.legend = FALSE) 




ggplot(data=data2,aes(x=Array_SNR,y=mean_peak_read_density,color=SeqClass))+ 
  geom_point(alpha=0.5) + 
  theme_bw() +
  facet_wrap(~SeqClass, nrow=1) + 
  ylab('Mean read density, K562') +
  xlab('Array SNR')+
  theme(aspect.ratio=1) + 
  ggpubr::stat_cor(aes(label = after_stat(r.label)), label.x = 30,label.y=350,show.legend = FALSE) 

```
